A Framework for Equivalence of Cast Calculi and a new Cast Representation

### 2020-10-09 paper.tex
comment

\begin{document}
%
\title{A Framework for Equivalence of Cast Calculi and a new Cast Representation}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Kuang-Chen Lu\inst{1} \and
Jeremy G. Siek\inst{2} \and
Andre Kuhlenschmidt\inst{2}
}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Brown University, Providence RI 02912, USA \and
Indiana University, Bloomington IN 47405, USA}
% \institute{Princeton University, Princeton NJ 08544, USA \and
% Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
% \email{lncs@springer.com}\\
% \url{http://www.springer.com/gp/computer-science/lncs} \and
% ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
% \email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Gradual typing aims at combining dynamic typing and static typing in one 
language to provide the advantages of both typing disciplines. Implementing 
gradual typing with reasonable overhead, however, is not trivial. Casts might 
accumulate in higher-order values and continuations, thus change the overall 
space complexity. Several space-efficient cast representations have been 
proposed, notably coercions in normal forms and threesomes. But they are
presented in different dynamic semantics, which make it difficult to compare
the key differences between the cast representations. We present a abstrat
data type, namely Cast ADT, that captures interface functions a cast representations
typically includes, and an abstract machine parameterized over Cast ADTs.
The Cast ADT brings another benefit: space-efficient cast representations 
shall be proved not changing the 
overall behavior of language implementations except saving space.
With our generic abstract machine, these proofs can be done by proving properties
of a specific Cast ADT, which is simpler than going through a bisimulation proof 
between a space-efficient dynamic semantics and the definitional dynamic semantics.
We have successfully applied our new approach of proving the correctness of cast 
representations to several known cast representations
(\cite{Siek:2010:TWB:1706299.1706342,siek2012interpretations,Siek:2015:BCT:2737924.2737968})
and believe this framework
is also applicable to other cast representations (\cite{Garcia:2013:CTB:2500365.2500603,siek2012interpretations}).
\todo[inline]{JS: cite which other cast representations}
\todo[inline]{KC: I am citing \cite{siek2012interpretations} for Lazy D coercions
in normal form, is this the right paper to cite?}
We also present a new cast representation, hypercoercions, that is more friendly
to mechanized meta-theory and consumes less memory than coercions
in normal forms.

@@

>>>>

\begin{document}
%
\title{A Framework for Equivalence of Cast Calculi and a new Cast Representation}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Kuang-Chen Lu\inst{1} \and
Jeremy G. Siek\inst{2} \and
Andre Kuhlenschmidt\inst{2}
}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Brown University, Providence RI 02912, USA \and
Indiana University, Bloomington IN 47405, USA}
% \institute{Princeton University, Princeton NJ 08544, USA \and
% Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
% \email{lncs@springer.com}\\
% \url{http://www.springer.com/gp/computer-science/lncs} \and
% ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
% \email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Gradual typing aims at combining dynamic typing and static typing in one 
language to provide the advantages of both typing disciplines. Implementing 
gradual typing with reasonable overhead, however, is not trivial. Casts might 
accumulate in higher-order values and continuations, thus change the overall 
space complexity. Several space-efficient cast representations have been 
proposed, notably coercions in normal forms and threesomes. But they are
presented in different dynamic semantics, which make it difficult to compare
the key differences between the cast representations. We present a abstrat
data type, namely Cast ADT, that captures interface functions a cast representations
typically includes, and an abstract machine parameterized over Cast ADTs.
The Cast ADT brings another benefit: space-efficient cast representations 
shall be proved not changing the 
overall behavior of language implementations except saving space.
With our generic abstract machine, these proofs can be done by proving properties
of a specific Cast ADT, which is simpler than going through a bisimulation proof 
between a space-efficient dynamic semantics and the definitional dynamic semantics.
We have successfully applied our new approach of proving the correctness of cast 
representations to several known cast representations
(\cite{Siek:2010:TWB:1706299.1706342,siek2012interpretations,Siek:2015:BCT:2737924.2737968})
and believe this framework
is also applicable to other cast representations (\cite{Garcia:2013:CTB:2500365.2500603,siek2012interpretations}).
We also present a new cast representation, hypercoercions, that is more friendly
to mechanized meta-theory and consumes less memory than coercions
in normal forms.

@@

\todo[inline]{JS: In the above you've lumped proxy-based and blame
  tracking together, which is incorrect. AFAIK,
  \cite{findler2002contracts} is the origin of blame tracking. AFAIK,
  \citet{Breazu-Tannen:1990vc} is the origin of proxy-based
  casts. (Who knows, there could be an even earlier paper for
  proxy-based casts, but that's the earliest one I know.)
  \citet{herman2010space} cited the wrong paper for function proxies,
  perhaps because they didn't know about the decade earlier
  \citet{Breazu-Tannen:1990vc}. Also, \cite{findler2002contracts}
  should have cited \citet{Breazu-Tannen:1990vc} but did not. Perhaps
  because they did not consider that papers about ``casts'' to be
  closely related to their paper about ``contracts''.  Or perhaps they
  too did not know about \citet{Breazu-Tannen:1990vc}.  Authors make
  mistakes all the time regarding related work, and this is just yet
  another example of that. For that matter, I should have cited
  \citet{Breazu-Tannen:1990vc} in \citet{siek2006gradual} but did not,
  probably because I had learned about it from the TAPL textbook
  (section 15.6) and therefore thought it was so standard that it
  didn't need a citation.  But it would have been better for me to
  cite it.}
